\section{Related Work}
The literature on object detection is vast. Before the success of deep convolutional neural networks~\cite{krizhevsky2012imagenet}, the widely used detection systems are based on a combination of independent components. First, handcrafted image features such as HOG~\cite{dalal2005histograms,zhang2011boosted,yu2010object}, SIFT~\cite{lowe2004distinctive}, and Fisher Vector~\cite{cinbis2013segmentation} are extracted at every location and scale of an image, usually through an image pyramid~\cite{lazebnik2006beyond}. Second, object models such as pictorial structure model (PSM)~\cite{felzenszwalb2005pictorial} and deformable part-based model (DPM)~\cite{felzenszwalb2010object, zhu2012face, yang2013articulated} allow object parts (e.g. head, torso, arms and legs of human) to deform with geometric constraints. Finally, a classifier such as boosting methods~\cite{viola2004robust}, linear SVM~\cite{dalal2005histograms}, latent SVM~\cite{felzenszwalb2010object}, or random forests~\cite{dollar2012crosstalk} determines whether the existence of a target object in a candidate window holds. 

The application of neural networks for detection tasks such as face detection also has a long history. The first work may date back to early in 1994 when Vaillant et al.~\cite{vaillant1994original} proposed to train a convolutional neural network to detect face in image window. Later in 1996 and 1998 Rowley et al.~\cite{rowley1998neural,rowley1998rotation} presented neural network based face detection systems to detect upright frontal face in image pyramid. There is no way to compare the performance of those ancient detectors with today’s detection systems on face detection benchmarks. Even so, they are still worth revisiting, as we find many similarities in design with our DenseBox. 

Recently, several papers propose algorithms of using deep convolutional neural networks for locating objects~\cite{sermanet2013overfeat, erhan2014scalable, YOLO}. OverFeat~\cite{sermanet2013overfeat} train a convolutional layer to predict the box coordinates for multiple class-specific objects from an image pyramid. MultiBox~\cite{erhan2014scalable} generate region proposals from a network whose output layer simultaneously predicts multiple boxes, which are used for R-CNN~\cite{girshick2014rich} object detection. YOLO~\cite{YOLO} also predicts bounding boxes and class probabilities directly from full images in one evaluation. All these methods use shared computation of convolutions~\cite{sermanet2013overfeat, he2014spatial, ren2015faster, long2015fully} which has been attracting increasing attention for efficient, yet accurate, visual recognition. 

However, most state-of-the-art object detection approaches~\cite{ouyang2014deepid, li2015convolutional, erhan2014scalable,girshick2015fast,yan2015object} rely on R-CNN, which divides detection into two steps: salient object proposal generation and region proposal classification. Several recent works such as YOLO and Faster R-CNN have jointed region proposal generation with classifier in one stage or two stages. It is pointed out by~\cite{farfade2015multi} that R-CNN with general proposal methods designed for general object detection could results in inferior performance in detection task such as face detection, due to loss recall for small-sized faces and faces in complex appearance variations. They share similarities with our method, and we will discuss them with our method in more detail in later context.  

Object detection is often involved with multi-task learning such as landmark localization, pose estimation and semantic segmentation. Zhu et al.~\cite{zhu2012face} propose a tree structure deformable part model for joint face detection, pose estimation and landmark localization. Deep net based object detection systems are also natural for integrating multi-task learning. Devries et al.~\cite{devries2014multi} learn facial landmarks and expressions simultaneously through deep neural networks. Sijin et al.~\cite{li2014heterogeneous} simultaneously learn pose joint regressor and sliding window body part detector in a deep network architecture. In this work, we integrate landmark localization into the object detection framework. 
